---
title: "Survey Analysis"
output:
  html_document: default
  html_notebook: default
  word_document: default
---

```{r, echo=FALSE}

#Load libraries

suppressMessages(library(xlsx))
suppressMessages(library(dplyr))
suppressMessages(library(tidyr))
suppressMessages(library(ggplot2))

```

```{r, echo=FALSE}

#Load respondents and other data

respondents <- read.xlsx2("US & Canada Employee Survey Data.xls", 1)

#Pre-analysis tidying
#Order Q1: What is your company size?
respondents$What.is.your.company.size. <- ordered(respondents$What.is.your.company.size., levels = c("1 (self employed)","2 to 500 employees","501 to 1,000 employees","1,001 to 5,000 employees Over 5,000 employees","Over 5,000 employees"), exclude = NULL)

```


## Category:
#### What is the state of Employee Engagement?

### Analysis:

Q5: Overall, how would you rate your work experience at your company?  
Rating from 1 - 5  
  
Q6: If asked about your company as a place to work, what kind of recommendation would you provide?  
Rating from 1 - 5  
  
Q7: How likely are you to remain an employee of your company over the next six months?  
Rating from 1 - 5  
  
#### Highengaged are those who score 4 or 5 on all 3 outcome variables (Q5, Q6, Q7)
#### Lowengaged are those who score 1 or 2 on all 3 outcome variables (Q5, Q6, Q7)
#### Lowengaged_new are those who score 1,2 or 3 on all 3 outcome variables (Q5, Q6, Q7)
#### Toxic are those who score 1 or 2 on Q5, 1, 2 or 3 on Q6 BUT score 5 or 6 on Q7
#### Toxic_new are those who score 1,2 or 3 on Q5, 1, 2 or 3 on Q6 BUT score 3, 4 or 5 on Q7

```{r, echo=FALSE}
respondents <- respondents %>%
# create highengaged variable
  mutate(highengaged = as.numeric(respondents$Overall..how.would.you.rate.your.work.experience.at.your.company....) > 3 & as.numeric(respondents$If.asked.about.your.company.as.a.place.to.work..what.kind.of.recommendation.would.you.provide.) >3 & as.numeric(respondents$How.likely.are.you.to.remain.an.employee.of.your.company.over.the.next.six.months.) >3) %>%
# create lowengaged variable
  mutate(lowengaged = as.numeric(respondents$Overall..how.would.you.rate.your.work.experience.at.your.company....) < 3 & as.numeric(respondents$If.asked.about.your.company.as.a.place.to.work..what.kind.of.recommendation.would.you.provide.) < 3 & as.numeric(respondents$How.likely.are.you.to.remain.an.employee.of.your.company.over.the.next.six.months.) < 3) %>%
# create lowengaged_new variable
  mutate(lowengaged_new = as.numeric(respondents$Overall..how.would.you.rate.your.work.experience.at.your.company....) < 4 & as.numeric(respondents$If.asked.about.your.company.as.a.place.to.work..what.kind.of.recommendation.would.you.provide.) < 4 & as.numeric(respondents$How.likely.are.you.to.remain.an.employee.of.your.company.over.the.next.six.months.) < 4) %>%
# create toxic variable
  mutate(toxic = as.numeric(respondents$Overall..how.would.you.rate.your.work.experience.at.your.company....) < 3 & as.numeric(respondents$If.asked.about.your.company.as.a.place.to.work..what.kind.of.recommendation.would.you.provide.) < 4 & as.numeric(respondents$How.likely.are.you.to.remain.an.employee.of.your.company.over.the.next.six.months.) > 3) %>%
# create toxic_new variable
  mutate(toxic_new = as.numeric(respondents$Overall..how.would.you.rate.your.work.experience.at.your.company....) < 4 & as.numeric(respondents$If.asked.about.your.company.as.a.place.to.work..what.kind.of.recommendation.would.you.provide.) < 4 & as.numeric(respondents$How.likely.are.you.to.remain.an.employee.of.your.company.over.the.next.six.months.) > 2)

hlt_summary <- respondents %>%
  select(highengaged, lowengaged, lowengaged_new, toxic, toxic_new) %>%
  gather(type, answer) %>%
  group_by(type, answer) %>%
  summarize(count = n()) %>%
  mutate(freq = count / sum(count))

```

```{r, echo=FALSE}

hlt_summary

ggplot(hlt_summary, aes(fill=answer, y=count, x=type)) + 
    geom_bar( stat="identity")

```


### Analysis:
Regression analysis of Q9 attributes on Q5

```{r, echo=FALSE}

# Make Q5 factor ordered
respondents$Overall..how.would.you.rate.your.work.experience.at.your.company.... <- ordered(respondents$Overall..how.would.you.rate.your.work.experience.at.your.company...., levels = c("Poor","Fair","Good","Very Good","Excellent"), exclude = NULL)

# Make Q6 factor ordered
respondents$If.asked.about.your.company.as.a.place.to.work..what.kind.of.recommendation.would.you.provide. <- ordered(respondents$If.asked.about.your.company.as.a.place.to.work..what.kind.of.recommendation.would.you.provide., levels = c("Very negative","Negative","Neutral","Positive","Very positive"), exclude = NULL)

# Make Q7 factor ordered
respondents$How.likely.are.you.to.remain.an.employee.of.your.company.over.the.next.six.months. <- ordered(respondents$How.likely.are.you.to.remain.an.employee.of.your.company.over.the.next.six.months., levels = c("Very Unlikely","Unlikely","Somewhat Likely","Likely","Very Likely"), exclude = NULL)

colnames(respondents) <- gsub('Overall..how.would.you.rate.your.work.experience.at.your.company....', 'rate_your_work', colnames(respondents), fixed=TRUE)

colnames(respondents) <- gsub('If.asked.about.your.company.as.a.place.to.work..what.kind.of.recommendation.would.you.provide.', 'reccommendation_on_work_', colnames(respondents), fixed=TRUE)

colnames(respondents) <- gsub('How.likely.are.you.to.remain.an.employee.of.your.company.over.the.next.six.months.', 'likely_to_remain', colnames(respondents), fixed=TRUE)

colnames(respondents) <- gsub('Please.rate.your.experience.at.your.workplace.on.the.following.attributes....', 'rate_experience_', colnames(respondents), fixed=TRUE)

# Make Q9 factor ordered
respondents[,19] <- ordered(respondents[,19], levels = c("Poor","Fair","Good","Very Good","Excellent"), exclude = NULL)

respondents[,20] <- ordered(respondents[,20], levels = c("Poor","Fair","Good","Very Good","Excellent"), exclude = NULL)

respondents[,21] <- ordered(respondents[,21], levels = c("Poor","Fair","Good","Very Good","Excellent"), exclude = NULL)

respondents[,22] <- ordered(respondents[,22], levels = c("Poor","Fair","Good","Very Good","Excellent"), exclude = NULL)

respondents[,23] <- ordered(respondents[,23], levels = c("Poor","Fair","Good","Very Good","Excellent"), exclude = NULL)

respondents[,24] <- ordered(respondents[,24], levels = c("Poor","Fair","Good","Very Good","Excellent"), exclude = NULL)

respondents[,25] <- ordered(respondents[,25], levels = c("Poor","Fair","Good","Very Good","Excellent"), exclude = NULL)

respondents[,26] <- ordered(respondents[,26], levels = c("Poor","Fair","Good","Very Good","Excellent"), exclude = NULL)

respondents[,27] <- ordered(respondents[,27], levels = c("Poor","Fair","Good","Very Good","Excellent"), exclude = NULL)

respondents[,28] <- ordered(respondents[,28], levels = c("Poor","Fair","Good","Very Good","Excellent"), exclude = NULL)

```

```{r}
summary(lm(as.numeric(respondents$rate_your_work)~.,data = data.frame(data.matrix(respondents[,c(19:28)]))))

ggplot(respondents, aes(x=as.numeric(respondents[,19]), y=as.numeric(rate_your_work))) + geom_point(shape=1) +  geom_smooth(method=lm , color="red", se=FALSE) + geom_count()

ggplot(respondents, aes(x=as.numeric(respondents[,20]), y=as.numeric(rate_your_work))) + geom_point(shape=1) +  geom_smooth(method=lm , color="red", se=FALSE) + geom_count()

ggplot(respondents, aes(x=as.numeric(respondents[,21]), y=as.numeric(rate_your_work))) + geom_point(shape=1) +  geom_smooth(method=lm , color="red", se=FALSE) + geom_count()

ggplot(respondents, aes(x=as.numeric(respondents[,22]), y=as.numeric(rate_your_work))) + geom_point(shape=1) +  geom_smooth(method=lm , color="red", se=FALSE) + geom_count()

ggplot(respondents, aes(x=as.numeric(respondents[,23]), y=as.numeric(rate_your_work))) + geom_point(shape=1) +  geom_smooth(method=lm , color="red", se=FALSE) + geom_count()

ggplot(respondents, aes(x=as.numeric(respondents[,24]), y=as.numeric(rate_your_work))) + geom_point(shape=1) +  geom_smooth(method=lm , color="red", se=FALSE) + geom_count()

ggplot(respondents, aes(x=as.numeric(respondents[,25]), y=as.numeric(rate_your_work))) + geom_point(shape=1) +  geom_smooth(method=lm , color="red", se=FALSE) + geom_count()

ggplot(respondents, aes(x=as.numeric(respondents[,26]), y=as.numeric(rate_your_work))) + geom_point(shape=1) +  geom_smooth(method=lm , color="red", se=FALSE) + geom_count()

ggplot(respondents, aes(x=as.numeric(respondents[,27]), y=as.numeric(rate_your_work))) + geom_point(shape=1) +  geom_smooth(method=lm , color="red", se=FALSE) + geom_count()

ggplot(respondents, aes(x=as.numeric(respondents[,28]), y=as.numeric(rate_your_work))) + geom_point(shape=1) +  geom_smooth(method=lm , color="red", se=FALSE) + geom_count()


summary(lm(as.numeric(respondents$reccommendation_on_work_)~.,data = data.frame(data.matrix(respondents[,c(19:28)]))))

summary(lm(as.numeric(respondents$likely_to_remain)~.,data = data.frame(data.matrix(respondents[,c(19:28)]))))

```


## Category:
What is the state of workplace communications?

### Analysis:
Descriptive statistics on Q8 (one graph), Q10 (one graph)
Q8: How would you rate your company in terms of digital technology adoption for internal communications?
Q10: There are many ways to communicate and have your opinion heard in a company. We would like you
to rate the effectiveness of each of the following in your company:
```{r, echo=FALSE}

# Q8 
# Description of the vector
#str(respondents$How.would.you.rate.your.company.in.terms.of.digital.technology.adoption.for.internal.communications.)
# Make Q8 factor ordered
respondents$How.would.you.rate.your.company.in.terms.of.digital.technology.adoption.for.internal.communications. <- ordered(respondents$How.would.you.rate.your.company.in.terms.of.digital.technology.adoption.for.internal.communications., levels = c("Poor","Fair","Good","Very Good","Excellent"), exclude = NULL)
# display percentages
respondents %>%
  group_by(How.would.you.rate.your.company.in.terms.of.digital.technology.adoption.for.internal.communications.) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  rename(internalAdoptionRating = How.would.you.rate.your.company.in.terms.of.digital.technology.adoption.for.internal.communications.)

# Q10
# Description of the data frame
#str(respondents[,29:37])
# Summary of the data frame
#summary(respondents[,29:37])

colnames(respondents) <- gsub('There.are.many.ways.to.communicate.and.have.your.opinion.heard.in.a.company..We.would.like.you.to.rate.the.effectiveness.of.each.of.the.following.in.your.company....', 'effective_with_', colnames(respondents), fixed=TRUE)

# Order Q10 columns
respondents[,29] <- ordered(respondents[,29], levels = c("Not applicable / Don't know","Not at all effective","Slightly effective","Moderately effective","Effective","Very effective"), exclude = NULL)

respondents[,30] <- ordered(respondents[,30], levels = c("Not applicable / Don't know","Not at all effective","Slightly effective","Moderately effective","Effective","Very effective"), exclude = NULL)

respondents[,31] <- ordered(respondents[,31], levels = c("Not applicable / Don't know","Not at all effective","Slightly effective","Moderately effective","Effective","Very effective"), exclude = NULL)

respondents[,32] <- ordered(respondents[,32], levels = c("Not applicable / Don't know","Not at all effective","Slightly effective","Moderately effective","Effective","Very effective"), exclude = NULL)

respondents[,33] <- ordered(respondents[,33], levels = c("Not applicable / Don't know","Not at all effective","Slightly effective","Moderately effective","Effective","Very effective"), exclude = NULL)

respondents[,34] <- ordered(respondents[,34], levels = c("Not applicable / Don't know","Not at all effective","Slightly effective","Moderately effective","Effective","Very effective"), exclude = NULL)

respondents[,35] <- ordered(respondents[,35], levels = c("Not applicable / Don't know","Not at all effective","Slightly effective","Moderately effective","Effective","Very effective"), exclude = NULL)

respondents[,36] <- ordered(respondents[,36], levels = c("Not applicable / Don't know","Not at all effective","Slightly effective","Moderately effective","Effective","Very effective"), exclude = NULL)

respondents[,37] <- ordered(respondents[,37], levels = c("Not applicable / Don't know","Not at all effective","Slightly effective","Moderately effective","Effective","Very effective"), exclude = NULL)

names(respondents[,29:37]) <- substring(names(respondents[,29:37]), 1, 42)

effective_with_summary <- respondents %>%
  select(29:37) %>%
  gather(effective_with_, answer) %>%
  group_by(effective_with_, answer) %>%
  summarize(count = n()) %>%
  mutate(freq = count / sum(count))

```

```{r}

ggplot(respondents, aes(x=as.factor(How.would.you.rate.your.company.in.terms.of.digital.technology.adoption.for.internal.communications.) )) + geom_bar()

# Display Percentages: Email
respondents %>%
  group_by(effective_with_Email..including.company.newsletters..etc..) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) #%>%

# Display Percentages: DocManagement
respondents %>%
  group_by(effective_with_Document.management.platform..e.g...Sharepoint..Google.for.Work.) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n)) #%>%

# Display Percentages: Survey
respondents %>%
  group_by(effective_with_Attitude...Engagement...Feedback.Surveys) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

# Display Percentages: SocialNetworkToolsInternally
respondents %>%
  group_by(effective_with_Social.Network.tools.used.internally..e.g...Yammer..Chatter..FaceBook.for.Work.) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

# Display Percentages: SocialNetworkToolsExternally
respondents %>%
  group_by(effective_with_Social.Network.tools.used.externally..e.g...Facebook..LinkedIn..Instagram..Snapchat.) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

# Display Percentages: EnterpriseCollabTools
respondents %>%
  group_by(effective_with_Enterprise.collaboration.tools..e.g...Slack..Chatter.) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

# Display Percentages: Blog
respondents %>%
  group_by(effective_with_Blogs...Microblogs) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

# Display Percentages: Wiki
respondents %>%
  group_by(effective_with_Company.Wikis) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

# Display Percentages: Content Sharing Communities
respondents %>%
  group_by(effective_with_Content.Sharing.Communities) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

ggplot(effective_with_summary, aes(fill=answer, y=count, x=effective_with_),order=answer) + 
    geom_bar( stat="identity")

```


### Analysis:
 New 3 points variable of "Effective" which classifies as follows: (average  of GT or EQ 4 across all Q10 = 3, average of  LT or EQ 2 across all Q10 = 1, ELSE = 2)

```{r, echo=FALSE}

# Store size of respondents
numFeatrures <- ncol(respondents)

# Get values of ordinal factors
for(i in 29:37) {
  respondents[,ncol(respondents) + 1] <- as.integer(respondents[,i])
}

# Get averages of answers to Q10 columns
respondents <- transform(respondents, Q10Averages = rowMeans(respondents[,148:156], na.rm = TRUE))

# Set the Effective Variable values
respondents$Effective <- ifelse(respondents$Q10Averages >= 3, 3, ifelse(respondents$Q10Averages <= 2, 1, 2))

```

```{r}
# Display Percentages: Effective
respondents %>%
  group_by(as.factor(Effective)) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

ggplot(respondents, aes(x=as.factor(Effective) )) + geom_bar()

```

### Analysis:
Relationship of "Effective" with "Highengaged", "Lowengaged" and "Toxic"

```{r, echo=FALSE}

effective_hlt_summary <- respondents %>%
  select(Effective, highengaged, lowengaged, lowengaged_new, toxic, toxic_new) %>%
  gather(engagement_type, answer, -Effective) %>%
  group_by(engagement_type, Effective) %>%
  summarize(count = sum(answer))

```

```{r}

ftable(respondents$Effective, respondents$highengaged)
ftable(respondents$Effective, respondents$lowengaged)
ftable(respondents$Effective, respondents$lowengaged_new)
ftable(respondents$Effective, respondents$toxic)
ftable(respondents$Effective, respondents$toxic_new)

ggplot(effective_hlt_summary, aes(fill=engagement_type, y=count, x=Effective)) + 
    geom_bar( stat="identity")

```


## Category:
Encouragement of Social Media in the workplace

### Analysis:
Descriptive statistics on Q21 thru Q27, including rank ordering Q21, Q24, Q25, Q27
 
Q21: Does your company encourage the use of the following social media sites for business use? (check all that apply)

```{r}

colnames(respondents) <- gsub('Does.your.company.encourage.the.use.of.the.following.social.media.sites.for.business.use...check.all.that.apply....', 'encourage_using_', colnames(respondents), fixed=TRUE)

encourage_using_summary <- respondents %>%
  select(grepl("encourage_using_", names(encourage_using_summary))) %>%
  gather(engagement_type, answer, -Effective) %>%
  group_by(engagement_type, Effective) %>%
  summarize(count = sum(answer))


# Display Percentages: LinkedIn
encourage_using_LinkedIn <- respondents %>%
  group_by(encourage_using_LinkedIn) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

encourage_using_LinkedIn <- respondents %>%
  group_by(encourage_using_Facebook) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

encourage_using_LinkedIn <- respondents %>%
  group_by(encourage_using_Instagram) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

encourage_using_LinkedIn <- respondents %>%
  group_by(encourage_using_Medium) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

encourage_using_LinkedIn <- respondents %>%
  group_by(encourage_using_Pinterest) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

encourage_using_LinkedIn <- respondents %>%
  group_by(encourage_using_Quora) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

encourage_using_LinkedIn <- respondents %>%
  group_by(encourage_using_Snapchat) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

encourage_using_LinkedIn <- respondents %>%
  group_by(encourage_using_Twitter) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

encourage_using_LinkedIn <- respondents %>%
  group_by(encourage_using_Youtube) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))


```


Q22: Are you encouraged to share your company's social postings on your personal social networks?

```{r}

colnames(respondents) <- gsub('Are.you.encouraged.to.share.your.company.s.social.postings.on.your.personal.social.networks.', 'encouragedPersonalNetworkSharing', colnames(respondents), fixed=TRUE)

respondents %>%
  group_by(encouragedPersonalNetworkSharing) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

```


Q23: How have you done it?

```{r}

colnames(respondents) <- gsub('How.have.you.done.it....', 'shared_by_', colnames(respondents), fixed=TRUE)

respondents %>%
  group_by(shared_by_Copied.and.pasted.from.email) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(shared_by_Copied.and.pasted.from.website) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

colnames(respondents) <- gsub('shared_by_Retweeted.shared.from.official.company.channels..e.g...website.', 'shared_by_Retweeted', colnames(respondents), fixed=TRUE)

respondents %>%
  group_by(shared_by_Retweeted) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(shared_by_Other..please.specify.) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(shared_by_I.have.not.done.it) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

```


Q24: In what ways have you participated in the use of social media for your workplace? (check all that apply)

```{r}

colnames(respondents) <- gsub('In.what.ways.have.you.participated.in.the.use.of.social.media.for.your.workplace...check.all.that.apply....', 'participated_by_', colnames(respondents), fixed=TRUE)

respondents %>%
  group_by(participated_by_Been.recommended.by.my.colleagues) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(participated_by_Communicated.major.changes.in.our.company) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(participated_by_Defended.employer.to.family.and.friends) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(participated_by_Defended.employer.where.others.could.see.or.read.it) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(participated_by_Encouraged.others.to.buy.company.s.products.or.services) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(participated_by_I.have.not.participated) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(participated_by_Made.positive.comments.about.employer.to.friends.or.family) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(participated_by_Made.positive.comments.about.employer.where.others.could.see.or.read.them) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(participated_by_Other..please.specify.) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))


```

Q25: Which of the following are you most likely to share on your personal social media about your workplace? [check all that apply]

```{r}

colnames(respondents) <- gsub('Which.of.the.following.are.you.most.likely.to.share.on.your.personal.social.media.about.your.workplace...check.all.that.apply....', 'most_likely_to_share_', colnames(respondents), fixed=TRUE)

respondents %>%
  group_by(most_likely_to_share_Company.achievements) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(most_likely_to_share_Company.mentions.in.the.news) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(most_likely_to_share_Contests) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(most_likely_to_share_Corporate.Social.Responsibility) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(most_likely_to_share_Events.organized.by.the.company) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(most_likely_to_share_Industry.news) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(most_likely_to_share_My.achievements) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(most_likely_to_share_Other..please.specify.) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(most_likely_to_share_Peer.achievements) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(most_likely_to_share_Promotional.messages) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

```

Q26: Are you allowed to share company content and add your own commentary to your company's social media shares?

```{r}

colnames(respondents) <- gsub('Are.you.allowed.to.share.company.content.and.add.your.own.commentary.to.your.company.s.social.media.shares.', 'allowed_to_share', colnames(respondents), fixed=TRUE)

respondents %>%
  group_by(allowed_to_share) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))


```


Q27: Which of the following would encourage you to share more about your workplace? (check all that apply)

```{r}

colnames(respondents) <- gsub('Which.of.the.following.would.encourage.you.to.share.more.about.your.workplace...check.all.that.apply....', 'encourage_me_to_share_by_', colnames(respondents), fixed=TRUE)

respondents %>%
  group_by(encourage_me_to_share_by_An.ability.to.comment) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(encourage_me_to_share_by_An.easy.interface) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(encourage_me_to_share_by_Good.visual.images) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(encourage_me_to_share_by_Relevant.content) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(encourage_me_to_share_by_None.of.the.above) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

```


### Analysis:
find any interesting (stand out) relationships between demos in Q1, Q3 and the attributes Q22, Q26

Q1: What is your company size?

vs
Q22: Are you encouraged to share your company's social postings on your personal social networks?
```{r}

ftable(respondents$What.is.your.company.size.,respondents$encouragedPersonalNetworkSharing)

```

vs
Q26: Are you allowed to share company content and add your own commentary to your company's social media shares?

```{r}

ftable(respondents$What.is.your.company.size.,respondents$allowed_to_share)

```


Q3: Which would you describe your company as primarily?

vs
Q22: Are you encouraged to share your company's social postings on your personal social networks?

```{r}

ftable(respondents$Which.would.you.describe.your.company.as.primarily.,respondents$encouragedPersonalNetworkSharing)

```

vs
Q26: Are you allowed to share company content and add your own commentary to your company's social media shares?

```{r}

ftable(respondents$Which.would.you.describe.your.company.as.primarily.,respondents$allowed_to_share)

```


## Category:
Drivers of Social Media

### Analysis:
Descriptive statistics on 4s and 5s for Q31, Q32

Q31: When thinking about your company's social media postings, how would you rate them on the following qualities?

```{r}

colnames(respondents) <- gsub('When.thinking.about.your.company.s.social.media.postings..how.would.you.rate.them.on.the.following.qualities....', 'posting_qualities_of_', colnames(respondents), fixed=TRUE)

respondents[,126] <- ordered(respondents[,126], levels = c("Very poor","Poor","Average","Good","Excellent"), exclude = NULL)

respondents[,127] <- ordered(respondents[,127], levels = c("Very poor","Poor","Average","Good","Excellent"), exclude = NULL)

respondents[,128] <- ordered(respondents[,128], levels = c("Very poor","Poor","Average","Good","Excellent"), exclude = NULL)

respondents[,129] <- ordered(respondents[,129], levels = c("Very poor","Poor","Average","Good","Excellent"), exclude = NULL)

respondents[,130] <- ordered(respondents[,130], levels = c("Very poor","Poor","Average","Good","Excellent"), exclude = NULL)

respondents[,131] <- ordered(respondents[,131], levels = c("Very poor","Poor","Average","Good","Excellent"), exclude = NULL)

respondents %>%
  group_by(posting_qualities_of_Engaging.content) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(posting_qualities_of_High.quality.content) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(posting_qualities_of_Informative) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(posting_qualities_of_Interesting.appealing) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(posting_qualities_of_Relateable) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(posting_qualities_of_Timely.relevant) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

```

Q32: How active are the following employees on workplace relevant social media in your company?

```{r}

colnames(respondents) <- gsub('How.active.are.the.following.employees.on.workplace.relevant.social.media.in.your.company....', 'how_active_is_', colnames(respondents), fixed=TRUE)

respondents[,132] <- ordered(respondents[,132], levels = c("No activity","Somewhat active","Moderately active","Active","Very active","Don't know"), exclude = NULL)

respondents[,133] <- ordered(respondents[,133], levels = c("No activity","Somewhat active","Moderately active","Active","Very active","Don't know"), exclude = NULL)

respondents[,134] <- ordered(respondents[,134], levels = c("No activity","Somewhat active","Moderately active","Active","Very active","Don't know"), exclude = NULL)

respondents[,135] <- ordered(respondents[,135], levels = c("No activity","Somewhat active","Moderately active","Active","Very active","Don't know"), exclude = NULL)

respondents[,136] <- ordered(respondents[,136], levels = c("No activity","Somewhat active","Moderately active","Active","Very active","Don't know"), exclude = NULL)

respondents[,137] <- ordered(respondents[,137], levels = c("No activity","Somewhat active","Moderately active","Active","Very active","Don't know"), exclude = NULL)

respondents[,138] <- ordered(respondents[,138], levels = c("No activity","Somewhat active","Moderately active","Active","Very active","Don't know"), exclude = NULL)

respondents[,139] <- ordered(respondents[,139], levels = c("No activity","Somewhat active","Moderately active","Active","Very active","Don't know"), exclude = NULL)

respondents[,140] <- ordered(respondents[,140], levels = c("No activity","Somewhat active","Moderately active","Active","Very active","Don't know"), exclude = NULL)

respondents %>%
  group_by(how_active_is_Corporate...Head.Office.employees) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(how_active_is_Corporate...Head.Office.managers) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(how_active_is_Customer.facing.employees) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(how_active_is_Customer.facing.managers) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(how_active_is_Directors.) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(how_active_is_Myself) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(how_active_is_President...CEO...Owner) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(how_active_is_Senior.Executives...C.Suite) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

respondents %>%
  group_by(how_active_is_Vice.Presidents) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))


```


### Analysis:
 Regression analysis of Q31 attributes on Q8

Q8: How would you rate your company in terms of digital technology adoption for internal communications?

Q31: When thinking about your company's social media postings, how would you rate them on the following qualities?

Q8 are rows
Q31 are columns

```{r}

summary(lm(How.would.you.rate.your.company.in.terms.of.digital.technology.adoption.for.internal.communications.~.,data = data.frame(data.matrix(respondents[,c(18,126:131)]))))

ftable(respondents$How.would.you.rate.your.company.in.terms.of.digital.technology.adoption.for.internal.communications.,respondents$posting_qualities_of_Interesting.appealing)

ftable(respondents$How.would.you.rate.your.company.in.terms.of.digital.technology.adoption.for.internal.communications.,respondents$posting_qualities_of_Relateable)

ftable(respondents$How.would.you.rate.your.company.in.terms.of.digital.technology.adoption.for.internal.communications.,respondents$posting_qualities_of_Informative)

ftable(respondents$How.would.you.rate.your.company.in.terms.of.digital.technology.adoption.for.internal.communications.,respondents$posting_qualities_of_Timely.relevant)

ftable(respondents$How.would.you.rate.your.company.in.terms.of.digital.technology.adoption.for.internal.communications.,respondents$posting_qualities_of_Engaging.content)

ftable(respondents$How.would.you.rate.your.company.in.terms.of.digital.technology.adoption.for.internal.communications.,respondents$posting_qualities_of_High.quality.content)

```

```{r, echo=FALSE}

write.xlsx(respondents, file="saif_employee.xlsx", sheetName="Data")

write.xlsx(respondents, file="saif_employee.xlsx", sheetName="Q18", append = TRUE)

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
